---
title: "IcoSem 2023"
description: |
  Iconicity Seminar 2023
site: distill::distill_website
---

```{r setup, include = FALSE}
library(knitr)
opts_chunk$set(echo = FALSE)
```

IcoSem 2023 will be held online on 25 November 2023 from GMT 7:00am to GMT 7:00pm.

This is equivalent to:

```{r echo = FALSE}
df <- 
  data.frame(City = c('Vancouver', 'Sao Paulo', 'Johannesburg', 'New Delhi', 'Tokyo'),
             From = c('24 Nov 11:00pm', '25 Nov 4:00am', '25 Nov 9:00am', '25 Nov 12:30pm', '25 Nov 4:00pm'),
             To = c('25 Nov 11:00am', '25 Nov 4:00pm', '25 Nov 9:00pm', '26 Nov 00:30am', '26 Nov 4:00am'))

kable(df)
```

This long time frame will allow participants all over the world in different time zones to participate in whichever time slot(s) they are available in.

The main language of the conference will be English, spoken and written with live transcription. Those wishing to present in a sign language are welcome do so, in which case English subtitles shall be provided.

# Call for papers

We call for papers for 30-minute presentations (20min presentation + 10min Q&A) dealing with any aspect of linguistic iconicity, such as:

* Sound symbolism
* Onomatopoeia and ideophones
* Sign language iconicity
* Syntactic iconicity
* Iconicity and language change
* Iconicity in writing systems
* Phonaesthetics
* Phonaesthemes

Please send a 2-page abstract (including everything) in the following format:

* A4 paper
* 2.5cm margin
* 12pt Times New Roman

Please send your anonymized abstract to [ian_joo@nucba.ac.jp](mailto:ian_joo@nucba.ac.jp). Your anonymous abstract will then be reviewed by two anonymous reviewers.

The deadline is September 30. Decisions will be communicated to you on a rolling basis within two weeks after submission.

There is no participation fee.

Join our [Facebook group for iconicity](https://www.facebook.com/groups/lingicon)
