---
title: "IcoSem3"
description: |
  The 3rd Iconicity Seminar
site: distill::distill_website
---

```{r setup, include = FALSE}
library(knitr)
library(readxl)
library(tidyverse)

opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')
```

The Iconicity Seminar (IcoSem) is an international conference dedicated to linguistic iconicity, the resemblance between linguistic form and meaning.

Previously an online conference, the 3rd IcoSem (IcoSem 3) will be held on 8-9 February 2025 in hybrid mode at the Otaru University of Commerce (Otaru, Japan).

# Program

All times are Japanese time.

## February 8: In-person presentations

```{r echo = FALSE}
papers <- 
  read_xlsx('IcoSem3ProgramInPerson.xlsx') %>% 
    mutate(Time = substr(Time, 12, 16))

kable(papers)
```

## February 9: Virtual presentations

```{r echo = FALSE}
papers <- 
  read_xlsx('IcoSem3ProgramVirtual.xlsx') %>% 
    mutate(Time = substr(Time, 12, 16))

kable(papers)
```

# Call for papers (closed)

We call for papers for 30-minute presentations (20min presentation + 10min Q&A) dealing with any aspect of linguistic iconicity, such as:

* Sound symbolism
* Onomatopoeia and ideophones
* Sign language iconicity
* Syntactic iconicity
* Iconicity and language change
* Iconicity in writing systems
* Phonaesthetics
* Phonaesthemes

Please send a 2-page abstract (including everything) in the following format:

* A4 paper
* 2.5cm margin
* 12pt Times New Roman

Please send your anonymized abstract to [joo@res.otaru-uc.ac.jp](mailto:joo@res.otaru-uc.ac.jp). Your anonymous abstract will then be reviewed by the organizer.

**The extended deadline is 31 October 2024**. Decisions will be communicated to you on a rolling basis as soon as possible.

Join our [Facebook group for iconicity](https://www.facebook.com/groups/lingicon)

# About Otaru

Otaru is a small coastal city in Hokkaido, the northernmost province of Japan. It is a popular tourist destination constantly rated as one of the most attractive Japanese cities. The Otaru Snow Light Path Festival will also take place in mid February, which the participants of the conference may be able to enjoy. The nearest airport is the New Chitose Airport (CTS), which has connections to several major Asian Pacific cities.